Project 1 Checkpoint

### 2015-02-06 project1/checkpoint/main.tex
Finishing up README
Some quick cleanup

\section{Problem Description}
Traffic simulation is becoming increasing important due to the expansion and growth of cities. Long-standing
infrastructure is forced to adapt in order to accomodate greater amounts of traffic, despite the fact that in many
cases the roads cannot be modified. This can be a result of legislation, existing buildings, and private property among
other things. So as a result, cities must instead optimize the variables they can control. In this case, we consider
signal light timing for the 12th St. and Peachtree Street intersection due to
time constraints, and the sheer difficulty with modeling traffic in general between multiple intersections. In particular,
we explore the effects that light timing has on traffic flow, given a source input distribution of cars.

\section{The Conceptual Model}
In order to create a representative software simulation of the aforementioned system, we first begin by designing a
conceptual version of this model from which we can plan our implementation. Data from \cite{cts12} was used extensively % TODO: Put this somewhere else
for modeling purposes in this project. Our architecture will be event driven, prioritizing events by timestamp. Furthermore,
we'll utilize the publisher-subscriber pattern (see \cite{pubsub}) to promote better decoupling.
Given this architecture, our first step will be to identify the entities present in our model, and then consider their
interactions (or the inherent ``activies'') within the simulation. This will allow us to then design the events that
are important

@@

\subsection{Simulation Input}
The two main sources of input into this simulation are the cars entering the section of Peachtree St with which we are
concerned, and the light timing of the system. The combination of these two variables are what influence the smoothness
of traffic flow to the actual drivers in the system.

@@

\begin{figure}
\begin{center}  
\includegraphics[width=4in]{../northbound.png}  
\caption{\small \sl Northbound Arrival Intervals \label{fig:northbound_arrival}}  
\end{center}  
\end{figure}

\begin{figure}  
\begin{center}
\includegraphics[width=4in]{../southbound.png}  
\caption{\small \sl Southbound Arrival Intervals \label{fig:southbound_arrival}}  
\end{center}  
\end{figure}

The distribution of car arrival is very important, but has been difficult to model. The arrival intervals between 
northbound and southbound cars are provided in \ref{fig:northbound_arrival} and \ref{fig:southbound_arrival}.
Model fitting was attempted for both $\Gamma$ and $\Gamma$ mixture models on the raw data, but resulted in poor
fits. Furthermore, pruning outliers via the common interquartile range approach, where values are rejected when
they lie outside of $median + 1.5IQR$, where $IQR$ is the interquartile range $Q_3 - Q_1$.

Given the difficulties with modelling we'll take a simpler approach and assume the ``true distribution`` is modeled by what was observed,
and simply use the observed frequency distribution as our input distribution. As the project progresses we can
refine this model.

@@

\subsubsection{Data Analysis}
In the \texttt{data\_processing} folder, most of code used for distribution fitting and statistics can be found there.
The data analysis code was written in Javascript, and runs completely in NodeJS \cite{nodejs}. NPM \cite{npm} was used
to manage dependencies and those dependencies can be seen in the \texttt{package.json} file. Of those packages, I have
authored the \texttt{chi-squared-test} module \cite{chiSquaredNpm}, and the \texttt{gamma-distribution}
\cite{gammaDistributionNpm}. Gulp \cite{gulp} was used a build tool for automating tasks (including building this paper).

@@

The simulation is written in CoffeeScript \cite{coffeescript}, which is a small language that compiles to JavaScript.
CoffeeScripts removes some of the boilerplate associated with setting up prototype chains and other object-oriented
concepts in JavaScript.
Backbone \cite{backbone} along with Underscore \cite{underscore} and jQuery \cite{jquery} were used to provide some
application structure, like basic eventing, and the sorted
collections that are used to form the basis for the event queue and \texttt{IntersectionQueue}. Lastly, Browserify
\cite{browserify} was used to bundle the code into a single file. Minification was done with Uglify.js \cite{uglify}.

\section{Current Build}
The simulation is currently deployed at \cite{aprilandchip} and currently runs a fixed number of cars through stepping
at 1 second real time being equal to 100ms. Eventually, this will be adjustable in real-time, and better visualized.

To build the application locally, you'll need to install a version of node at 0.10.0 or higher. This will be bundled
with npm. Since this project uses gulp for a task runner, you'll need to install it globally via
\texttt{npm install -g gulp}. Inside the \texttt{simulation} directory, you'll need to pull in packages with just
\texttt{npm install}. Once that installs, running \texttt{gulp} will run the build for you and generate a
\texttt{main.js} that's included in the \texttt{index.html} file. Opening this file in a browser should run the
simulation.

>>>>

\section{Problem Description}
Traffic simulation is becoming increasing important due to the expansion and growth of cities. Long-standing
infrastructure is forced to adapt in order to accomodate greater amounts of traffic, despite the fact that in many
cases the roads cannot be modified. This can be a result of legislation, existing buildings, and private property among
other things. So as a result, cities must instead optimize the variables they can control. In this case, we consider
signal light timing for the 12th St. and Peachtree Street intersection. In particular,
we explore the effects that light timing has on traffic flow, given a source input distribution of cars.

\section{The Conceptual Model}
In order to create a representative software simulation of the aforementioned system, we first begin by designing a
conceptual version of this model from which we can plan our implementation. We'll borrow heavily from the results and data
in \cite{cts12} when formulating our model.
Our architecture will be event driven, prioritizing events by timestamp. Furthermore,
we'll utilize the publisher-subscriber pattern (see \cite{pubsub}) to promote better decoupling.
Given this architecture, our first step will be to identify the entities present in our model, and then consider their
interactions (or the inherent ``activies'') within the simulation. This will allow us then to design the events that
are important

@@

\subsection{Simulation Input}
The two main sources of input into this simulation are the cars entering out section of Peachtree St, and the light
timing of the system. The combination of these two variables are what influence the smoothness
of traffic flow to the actual drivers in the system.

@@

\begin{figure}
\begin{center}  
\includegraphics[width=4in]{../northbound.png}  
\caption{\small \sl Northbound Arrival Intervals by Order of Occurrence\label{fig:northbound_arrival}}  
\end{center}  
\end{figure}

\begin{figure}  
\begin{center}
\includegraphics[width=4in]{../southbound.png}
\caption{\small \sl Southbound Arrival Intervals by Order of Occurrence\label{fig:southbound_arrival}}  
\end{center}  
\end{figure}

The distribution of car arrival is very important, but has been difficult to model. The arrival intervals between 
northbound and southbound cars are provided in \ref{fig:northbound_arrival} and \ref{fig:southbound_arrival}.
Model fitting was attempted for both $\Gamma$ and $\Gamma$-mixture models on the raw data, but resulted in poor
fits. Furthermore, pruning outliers via the common interquartile range approach, where values are rejected when
they lie outside of $median + 1.5IQR$, where $IQR$ is the interquartile range $Q_3 - Q_1$.

Given the difficulties with modelling we'll take a simpler approach and assume the ``true distribution`` is modeled by what was observed,
and simply plan to use the observed frequency distribution as our input distribution. As the project progresses we can
refine this model.

@@

\subsubsection{Data Analysis}
In the \texttt{data\_processing} folder, most of code used for distribution fitting and statistics can be found there.
The data analysis code was written in JavaScript, and runs completely in NodeJS \cite{nodejs}. NPM \cite{npm} was used
to manage dependencies and those dependencies can be seen in the \texttt{package.json} file. Of those packages, I have
authored the \texttt{chi-squared-test} module \cite{chiSquaredNpm}, and the \texttt{gamma-distribution}
\cite{gammaDistributionNpm}. Gulp \cite{gulp} was used a build tool for automating tasks (including building this paper).
To run some of the data analysis code I wrote, you'll need to install and run gulp. Instructions for doing so are
provided in the final section of this paper.

@@

The simulation is written in CoffeeScript \cite{coffeescript}, which is a small language that compiles to JavaScript.
CoffeeScript removes some of the boilerplate associated with setting up prototype chains and other object-oriented
concepts in JavaScript.
Backbone \cite{backbone} along with Underscore \cite{underscore} and jQuery \cite{jquery} were used to provide some
application structure, like basic eventing, and the sorted
collections that are used to form the basis for the event queue and \texttt{IntersectionQueue}. Lastly, Browserify
\cite{browserify} was used to bundle the code into a single file. Minification was done with Uglify.js \cite{uglify}.

\section{Current Build and Running Instructions}
The simulation is currently deployed at \cite{aprilandchip} and currently runs a fixed number of cars through stepping
at 1 second real time being equal to 100ms. Eventually, this will be adjustable in real-time, and better visualized.
Cars are generated regularly at 10 (+ an uniformly random number between 0 and 1) second intervals. Light timings are
currently hard-coded as well. Currently, we're only modeling a single direction, and ignoring turns, and variations
between cars.

To build the application locally, you'll need to install a version of Node.js \cite{nodejs} at 0.10.0 or higher. This will be bundled
with npm. Since this project uses gulp for a task runner, you'll need to install it globally via
\texttt{npm install -g gulp}. Inside the \texttt{simulation} directory, you'll need to pull in packages with just
\texttt{npm install}. Once that installs, running \texttt{gulp} will run the build for you and generate a
\texttt{main.js} that's included in the \texttt{index.html} file. Opening this file in a browser should run the
simulation.
